---
title:  "Experiment 2: Iterated Learning"
output: html_document
---

```{r setup, include=FALSE}
options(warn=-1)
library(tidyverse)
library(lubridate)
library(stringdist)
library(lme4)
library(lmerTest)
```

## Needed functions
Create dataframes for compehension tests and write-in data. 

```{r results='hide', message=FALSE, warning=FALSE}


analyze<- function(datas) {
  dataTesting <-list()
  scores <- c()
  for (i in 1:length(datas)) {
    dataTesting[[i]] <- datas[[i]][datas[[i]]$trialType == "testing",]
    dataTesting[[i]]$correct = dataTesting[[i]]$correctChoiceNumber == dataTesting[[i]]$participantChoiceNumber
  }
  return(dataTesting)
}

analyzeMeanTesting <- function(dataTesting) {
  dataTestingLevel <- list()
  for (i in 1:length(dataTesting)) {
    dataTestingLevel[[i]] <- dataTesting[[i]][!dataTesting[[i]]$level %in% c("ADP","OBJ"),]  %>%
      group_by(level)  %>% 
      summarize(level_score = sum(correct)/length(correct))
    dataTestingLevel[[i]]$chain <- rep(dataTesting[[i]]$chain[1], 2)
    dataTestingLevel[[i]]$generation <- rep(dataTesting[[i]]$generation[1], 2)
    dataTestingLevel[[i]]$user <- rep(dataTesting[[i]]$workerId[1], 2)
  }
  dataTestingLevelAllUsers <- rbind()
  for (dat in dataTestingLevel) {
    dataTestingLevelAllUsers <- rbind(dataTestingLevelAllUsers, dat)
  }
  return(dataTestingLevelAllUsers)
}

analyzeWriting <- function(datas) {
  #compositional answers analysis
  data_write <- list()
  data_write_level <- list()
  for (i in 1:length(datas)) {
    dataWriteNew <- datas[[i]][datas[[i]]$trialType == "write",]
    dataWriteNew$participantText <- as.character(dataWriteNew$participantText)
    dataWriteNew$participantText[is.na(dataWriteNew$participantText)] <- ""
      #print(dataWriteNew$participantText)
      data_write[[length(data_write) +1]] <- dataWriteNew
  }
  
  return (data_write)
}


```

## Processing the data

```{r results='hide', message=FALSE, warning=FALSE}
setwd("/Users/emilydavis/Desktop/paper data/Experiment2 iteration5gens")
dataAnon <- read.csv(paste0(getwd(), '/allDataAnonIter5.csv'))
dataFiles2 <- split(dataAnon, dataAnon$workerId)
chains <- toupper(letters)[1:12]
listAllChains<-read.csv(paste0(getwd(), '/allChainsIter5.csv'))
```

```{r message=FALSE, warning=FALSE}
allDataTesting <- analyze(dataFiles2)
allDataTestingMerged <- rbind()
for (dat in allDataTesting) {
  allDataTestingMerged <- rbind(allDataTestingMerged, dat)
}
allDataTestingLevel <- analyzeMeanTesting(allDataTesting)
allDataTestingMean <- allDataTestingLevel %>% group_by(chain, generation, level) %>% summarize(level_score = mean(level_score))

allDataWrite <- analyzeWriting(dataFiles2)
```

## Comprehension

Graph and analysis

```{r results='hide', message=FALSE, warning=FALSE}

ggplot(allDataTestingLevel, aes(x= generation+1, y= level_score, color = chain, alpha = .5)) +
  geom_line()+
  facet_wrap(~level, ncol=1)+
  scale_x_discrete(name ="generation", 
                    limits=1:5)+
  stat_summary(aes(colour="mean",group=1), fun.y= "mean", geom="line", color = "black", alpha = 1)+
   guides(alpha = FALSE)+
  ylab("Proportion correct")+
  theme_bw()+
  theme(legend.position = "none")

```

```{r message=FALSE, warning=FALSE}
library(MASS)

testLmerInteract <- glmer(correct ~ level* generation +(1 + level | chain:workerId) + (1 + generation | chain), data = allDataTestingMerged[allDataTestingMerged$level %in% c(2,3),], family = "binomial")
```

## Production accuracy

Combine all writing trials, and get initials. 

```{r message=FALSE, warning=FALSE}
allDataWriteNew <- list()
for (d in allDataWrite) {
encodingCorrected <- c()
for (i in 1:nrow(d)) {
  splitC <- strsplit(as.character(d$participantText[i]), " ")[[1]]
  initialsC <- c()
  for (word in splitC) {
    initialsC <- c(initialsC, substring(word, 1, 1))
  }
  initC <- paste(initialsC, collapse = "")
  encodingCorrected <- c(encodingCorrected, initC)
}
encodingCompositional <- c()
for (i in 1:nrow(d)) {
  splitC <- strsplit(as.character(d$compositionalAnswer[i]), " ")[[1]]
  initialsC <- c()
  for (word in splitC) {
    initialsC <- c(initialsC, substring(word, 1, 1))
  }
  initC <- paste(initialsC, collapse = "")
  encodingCompositional<- c(encodingCompositional, initC)
}
d <-cbind(d, encodingCorrected, encodingCompositional)
correctness <- c()
for (i in 1:nrow(d)) {
  longer = max( 
nchar(as.character(d$encodingCompositional[i])), nchar(as.character(d$encodingCorrected[i])) )
  normedC <- 1- (stringdist(as.character(d$encodingCompositional[i]),
                            as.character(d$encodingCorrected[i]),
                                      method = "osa")/longer)
  correctness <-c(correctness, normedC) 
}
d <- cbind(d, correctness)
allDataWriteNew[[length(allDataWriteNew)+1]] <- d
}

analyzeWritingMeans<- function (data_write) {
  data_write_level <- list()
  for (j in 1:length(data_write)) {
    data_write_level[[j]] <- data_write[[j]][data_write[[j]]$seenInTraining== "true",] %>% group_by(workerId, level, chain, generation, seenInTraining) %>% summarize(meanC = mean(correctness))
    data_write_level[[j]]$generation <- rep(data_write[[j]]$generation[1], 3)
    data_write_level[[j]]$chain <- rep(data_write[[j]]$chain[1], 3)
    data_write_level[[j]]$user<- rep(data_write[[j]]$workerId[1], 3)
  }
  
  data_write_levelAll <- rbind()
  for (d in data_write_level) {
    data_write_levelAll <- rbind(data_write_levelAll, d)
  }
  return (data_write_levelAll)
}

analyzeWritingMeansNovel<- function(dat, chains) {
  dat2<- rbind()
  for (j in 1:length(dat)) {
    dat2 <- rbind(dat2, dat[[j]])
  }
  dat2$compositionalAnswer <- as.character(dat2$compositionalAnswer)
  dat2$participantText <- as.character( dat2$participantText)
    for (c in chains) {
      for (n in c(10:2)) {#backwards through gens
        for (l in c(2:4)) {
        dat2$compositionalAnswer[dat2$trialType == "write" & dat2$chain == c & dat2$generation == n & dat2$level == l] <-
        dat2$participantText[dat2$trialType == "write" & dat2$chain == c & dat2$generation == n-1 & dat2$level == l]
        }
      }
    }

  d <- dat2[dat2$trialType == "write" & dat2$seenInTraining == "false",]
  encodingCorrected <- c()
for (i in 1:nrow(d)) {
  splitC <- strsplit(as.character(d$participantText[i]), " ")[[1]]
  initialsC <- c()
  for (word in splitC) {
    initialsC <- c(initialsC, substring(word, 1, 1))
  }
  initC <- paste(initialsC, collapse = "")
  encodingCorrected <- c(encodingCorrected, initC)
}
encodingCompositional <- c()
for (i in 1:nrow(d)) {
  splitC <- strsplit(as.character(d$compositionalAnswer[i]), " ")[[1]]
  initialsC <- c()
  for (word in splitC) {
    initialsC <- c(initialsC, substring(word, 1, 1))
  }
  initC <- paste(initialsC, collapse = "")
  encodingCompositional<- c(encodingCompositional, initC)
}
d <-cbind(d, encodingCorrected, encodingCompositional)
correctness <- c()
for (i in 1:nrow(d)) {
  longer = max( 
nchar(as.character(d$encodingCompositional[i])), nchar(as.character(d$encodingCorrected[i])) )
  normedC <- 1- (stringdist(as.character(d$encodingCompositional[i]),
                            as.character(d$encodingCorrected[i]),
                                      method = "osa")/longer)
  correctness <-c(correctness, normedC) 
}
d <- cbind(d, correctness)
  d2 <- split(d, d$workerId)
  for (j in 1:length(d2)) {
    d2[[j]] <- d2[[j]]%>% group_by(workerId, level, chain, generation, seenInTraining) %>% summarize(meanC = mean(correctness))
    d2[[j]]$generation <- rep(d2[[j]]$generation[1], 3)
    d2[[j]]$chain <- rep(d2[[j]]$chain[1], 3)
    d2[[j]]$user<- rep(d2[[j]]$workerId[1], 3)
  }
  
  data_write_levelAll <- rbind()
  for (d in d2) {
    data_write_levelAll <- rbind(data_write_levelAll, d)
  }
  return (data_write_levelAll)
  return(d)
}

allDataWriteMeans<- analyzeWritingMeans(allDataWriteNew)
allDataWriteMeansUnseen<- analyzeWritingMeansNovel(dataFiles2, chains)
```

```{r}
allDataWriteMeans2 <- rbind(allDataWriteMeans, allDataWriteMeansUnseen)
allDataWriteMeans2$seenInTraining <- as.character(allDataWriteMeans2$seenInTraining)
allDataWriteMeans2$seenInTraining[allDataWriteMeans2$seenInTraining == "true"] <- "seen"

allDataWriteMeans2$seenInTraining[allDataWriteMeans2$seenInTraining == "false"] <- "unseen"
ggplot(allDataWriteMeans2, aes(x= generation+1, y= meanC, color = chain, alpha = .5)) +
  geom_line()+
  stat_summary(aes(colour="mean",group=1), fun= "mean", geom="line", color = "black", alpha = 1)+
   guides(alpha = FALSE)+
    facet_grid(rows = vars(level), cols = vars(seenInTraining))+
  scale_x_discrete(name ="generation", 
                    limits=factor(1:5))+
   guides(alpha = FALSE)+
  ggtitle("")+ 
  ylab("Correctness")+
  theme_bw()+
  theme(legend.position = "none")
```


```{r  message=FALSE, warning=FALSE}
library(MASS)
allDataWriteMeans$level <- factor(allDataWriteMeans$level, levels = c(1,2,3))
allDataWriteMeansUnseen$level <- factor(allDataWriteMeansUnseen$level, levels = c(2,3,4))
contrasts(allDataWriteMeans$level) <- contr.sdif(3)
contrasts(allDataWriteMeansUnseen$level) <- contr.sdif(3)
modelConsistencySeen <- lmer(meanC ~ level* generation + (1+generation * level | chain), data = allDataWriteMeans)
modelConsistencyUnseen <- lmer(meanC ~  level* generation + (1+generation * level | chain), data = allDataWriteMeansUnseen)
```

## Analysis of writing: matching possible grammars 
Merge relevant columns of writing files into one big file, including Generation 0

```{r}
listAllWriteIns <- rbind()
listAllChains <- arrange(listAllChains, workerId) #Zero comes last
for (i in 1:nrow(listAllChains)) {
    workerId = listAllChains$workerId[i]
    if (str_detect(workerId, "Zero") == TRUE) {
      dt <- arrange(dataFiles2[[1]], time) #use as placeholder
    arrayTraining =unique(dt$arrayTraining[dt$trialType == "write"]) #get arrays in order listed
    time <- (40*i):(40*i+39)
    seen <- dt$seenInTraining[dt$trialType == "write"]
    } else {
    dt <- arrange(dataFiles2[[i]], time)
    arrayTraining =unique(dt$arrayTraining[dt$trialType == "write"])
    time <- dt$time[dt$trialType == "write"]
    seen <- dt$seenInTraining[dt$trialType == "write"]
    level <- dt$level[dt$trialType == "write"]
    }
  writeGen <- data.frame(workerId, gen = listAllChains$generation[i], chain = listAllChains$chain[i],
                         prepM = listAllChains$prepM[i], prepR = listAllChains$prepR[i], 
                         strings =strsplit(as.character(listAllChains$strings[i]), ";")[[1]], arrayTraining, time, seen, level)
listAllWriteIns <- rbind(listAllWriteIns, writeGen)
}
listAllWriteIns$strings <- as.character(listAllWriteIns$strings)
consonants <- c()
for (j in unique(listAllWriteIns$workerId)) {
  cns<- ''
   for (k in 0:3) {
    cns <- paste0(cns, strsplit(listAllWriteIns$strings[listAllWriteIns$workerId == j & listAllWriteIns$arrayTraining == k], '')[[1]][1])
   }
  consonants <- c(consonants, rep(cns, 40))
}

encodingCorrected <- c()
for (i in 1:nrow(listAllWriteIns)) {
  splitC <- strsplit(as.character(listAllWriteIns$strings[i]), " ")[[1]]
  initialsC <- c()
  for (word in splitC) {
    initialsC <- c(initialsC, substring(word, 1, 1))
  }
  initC <- paste(initialsC, collapse = "")
  encodingCorrected <- c(encodingCorrected, initC)
}
listAllWriteIns <- cbind(listAllWriteIns, encodingCorrected, consonants)
write.csv(listAllWriteIns, paste0(getwd(), '/writeInsIterNew.csv') )
```

Then run the python code (array to caption syntax orders.py) with appropriate input and output files. 

Output models to HTML
```{r  message=FALSE, warning=FALSE}
library(sjPlot)
a<- as.data.frame(coefficients(summary(testLmerInteract)))
rownames(a) <-gsub("Intercept", "level 2/generation 1", rownames(a))
rownames(a) <-gsub("level2", "level 3", rownames(a))
rownames(a) <-gsub(":", "/", rownames(a))

b<- as.data.frame(coefficients(summary(modelConsistencySeen)))
rownames(b) <-gsub("Intercept", "level 1/generation 0", rownames(b))
rownames(b) <-gsub(":", "/", rownames(b))

c<- as.data.frame(coefficients(summary(modelConsistencyUnseen)))
rownames(c) <-gsub("Intercept", "level 2/generation 1", rownames(c))
rownames(c) <-gsub(":", "/", rownames(c))
library(sjmisc)
allModels <- list(a, b,c)
for (i in 1:length(allModels)) {
  allModels[[i]] <- round_num(allModels[[i]], 3)
allModels[[i]][,ncol(allModels[[i]])][allModels[[i]][,ncol(allModels[[i]])] == 0] <- "< .001"
}
tab_dfs(allModels, titles = c("Comprehension task", "Consistency of captions: arrays seen in training", "Consistency of captions: novel arrays"), file = paste0 (getwd(),  '/tables.html') )
```