---
title: 'Experiment 1: Learnability (3 syntax conditions, adposition training)'
output:
  html_document: default
  word_document: default
---

```{r setup, message=FALSE, warning=FALSE}
options(warn=-1)
options(dplyr.summarise.inform = FALSE)
# install.packages("tidyverse", repo = 'https://mac.R-project.org')
#install.packages("sjPlot", repo = 'https://mac.R-project.org')
#install.packages("modelsummary")
library (tidyverse)
library(stringdist)
library(lme4)
library(lmerTest)
```

## Needed functions
Create dataframes for comprehension tests and write-in data. 

```{r results='hide', message=FALSE, warning=FALSE}

analyze<- function(datas) {
  dataTesting <-list()
  scores <- c()
  for (i in 1:length(datas)) {
    dataTesting[[i]] <- datas[[i]][datas[[i]]$trialType == "testing",]
    dataTesting[[i]]$correct = dataTesting[[i]]$correctChoiceNumber == dataTesting[[i]]$participantChoiceNumber
  }
  return(dataTesting)
}

analyzeMeanTesting <- function(dataTesting) {
  dataTestingLevel <- list()
  for (i in 1:length(dataTesting)) {
    dataTestingLevel[[i]] <- dataTesting[[i]][!dataTesting[[i]]$level %in% c("ADP","OBJ"),]  %>%
      group_by(level)  %>% 
      summarize(level_score = sum(correct)/length(correct))
    dataTestingLevel[[i]]$condition <- rep(dataTesting[[i]]$condition[1], 2)
    dataTestingLevel[[i]]$conditionCE <- rep(dataTesting[[i]]$conditionCE[1], 2)
    dataTestingLevel[[i]]$conditionHeadN <- rep(dataTesting[[i]]$conditionHeadN[1], 2)
    dataTestingLevel[[i]]$user <- rep(dataTesting[[i]]$workerId[1], 2)
  }
  dataTestingLevelAllUsers <- rbind()
  for (dat in dataTestingLevel) {
    dataTestingLevelAllUsers <- rbind(dataTestingLevelAllUsers, dat)
  }
  return(dataTestingLevelAllUsers)
}

analyzeWriting <- function(datas) {
  #compositional answers analysis
  data_write <- list()
  data_write_level <- list()
  for (i in 1:length(datas)) {
    dataWriteNew <- datas[[i]][datas[[i]]$trialType == "write",]
    dataWriteNew$participantText[is.na(dataWriteNew$participantText)] <- ""
      #print(dataWriteNew$participantText)
      
      data_write[[length(data_write) +1]] <- dataWriteNew
  }
  
  return (data_write)
}


```

## Processing the data
Import task data and demographic files, which have been anonymized. 

```{r results='hide', message=FALSE, warning=FALSE}
setwd("/Users/emilydavis/Downloads/paper data/Experiment1Learnability")
dataAnon <- read.csv(paste0(getwd(), '/allDataAnon.csv'))
prepList <- read.csv(paste0(getwd(), '/prepList.csv'))
#correct condition names so they show up correctly on all graphs
dataAnon$conditionCE[dataAnon$conditionCE == "no center-embedding"] <- "branching"
dataAnon$conditionHeadN[dataAnon$conditionHeadN == "head initial"] <- "noun initial"
dataAnon$conditionHeadN[dataAnon$conditionHeadN == "head final"] <- "noun final"
dataAnon$conditionCE <- factor(dataAnon$conditionCE)
dataFiles <- split(dataAnon, dataAnon$workerId)

allDataTesting <- analyze(dataFiles)
allDataTestingMerged <- rbind()
for (dat in allDataTesting) {
  allDataTestingMerged <- rbind(allDataTestingMerged, dat)
}
allDataTestingLevel <- analyzeMeanTesting(allDataTesting)
allDataTestingMean <- allDataTestingLevel %>% group_by(conditionCE, conditionHeadN, level) %>% summarize(level_score = mean(level_score))
allDataWrite <- analyzeWriting(dataFiles)
```



## Comprehension

Setting up for Helmert contrasts 

```{r}
#get CE and crossed together 
allDataTestingMerged$conditionCE <- as.character(allDataTestingMerged$conditionCE)

allDataTestingMerged$conditionHeadN <- as.character(allDataTestingMerged$conditionHeadN)
allDataTestingMerged$conditionHeadN <- factor(allDataTestingMerged$conditionHeadN)
allDataTestingMerged$conditionCE <- factor(allDataTestingMerged$conditionCE)
allDataTestingMerged$conditionCE <- relevel(allDataTestingMerged$conditionCE, "crossed")
allDataTestingMerged$conditionCE <- relevel(allDataTestingMerged$conditionCE, "center-embedding")
contrasts(allDataTestingMerged$conditionCE) <- contr.helmert(3)
contrasts(allDataTestingMerged$conditionHeadN) <- contr.sum(2)
```

Graph of comprehension task. 
```{r  message=FALSE, warning=FALSE}
allDataTestingLevel$level <- as.factor(allDataTestingLevel$level)
allDataTestingLevel$conditionHeadN <- as.factor(allDataTestingLevel$conditionHeadN)
allDataTestingLevel$conditionCE <- as.factor(allDataTestingLevel$conditionCE)

allDataTestingLevel$conditionHeadN <- relevel(allDataTestingLevel$conditionHeadN, "noun initial", "noun final")

allDataTestingLevel$conditionCE <- relevel(allDataTestingLevel$conditionCE, "crossed")
allDataTestingLevel$conditionCE <- relevel(allDataTestingLevel$conditionCE, "center-embedding")
library(scales)
colors <- hue_pal()(4)
ggplot(allDataTestingLevel, aes(x= level, y= level_score, fill = level))+
  stat_summary(aes(fill = level,group=1), fun= "mean", geom="point", pch = 23, size = 3) +
  geom_dotplot(binaxis='y',stackdir='center', alpha = .5)+
  facet_grid(conditionCE ~ conditionHeadN)+
  scale_x_discrete(name = "level", labels = c("2", "3"))+
    scale_fill_manual(values = colors[2:3] , labels = c("2", "3"), guide = FALSE)+
  ylab("Proportion correct")+
   theme_bw()
```

#Mixed effects model of correct-answer rates on comprehension tests by level. 
```{r  message=FALSE, warning=FALSE}
testLmerInteract2 <- glmer(correct ~ level* conditionCE * conditionHeadN + (1 +level|workerId), data = allDataTestingMerged[!allDataTestingMerged$level %in% c("ADP","OBJ"),], family = "binomial")
contrasts(allDataTestingMerged$conditionCE)
library(sjPlot)
```



## Production accuracy

Combine all writing trials, and get initials. 
```{r, message=FALSE, warning=FALSE}
allDataWriteNew <- list()
for (d in allDataWrite) {
encodingCorrected <- c()
for (i in 1:nrow(d)) {
  splitC <- strsplit(as.character(d$participantText[i]), " ")[[1]]
  initialsC <- c()
  for (word in splitC) {
    initialsC <- c(initialsC, substring(word, 1, 1))
  }
  initC <- paste(initialsC, collapse = "")
  encodingCorrected <- c(encodingCorrected, initC)
}
encodingCompositional <- c()
for (i in 1:nrow(d)) {
  splitC <- strsplit(as.character(d$compositionalAnswer[i]), " ")[[1]]
  initialsC <- c()
  for (word in splitC) {
    initialsC <- c(initialsC, substring(word, 1, 1))
  }
  initC <- paste(initialsC, collapse = "")
  encodingCompositional<- c(encodingCompositional, initC)
}
d <-cbind(d, encodingCorrected, encodingCompositional)
correctness <- c()
for (i in 1:nrow(d)) {
  longer = max( 
nchar(as.character(d$encodingCompositional[i])), nchar(as.character(d$encodingCorrected[i])) )
  normedC <- 1- (stringdist(as.character(d$encodingCompositional[i]),
                            as.character(d$encodingCorrected[i]),
                                      method = "osa")/longer)
  correctness <-c(correctness, normedC) 
}
d <- cbind(d, correctness)
d$level <- as.factor(d$level)
allDataWriteNew[[length(allDataWriteNew)+1]] <- d
}

analyzeWritingMeans<- function (data_write) {
  data_write_level <- list()
  for (j in 1:length(data_write)) {
    data_write_level[[j]] <- data_write[[j]][data_write[[j]]$seenInTraining== "true",] %>% group_by(workerId, level, conditionHeadN, conditionCE) %>% summarize(meanC = mean(correctness))
    data_write_level[[j]]$conditionCE <- rep(data_write[[j]]$conditionCE[1], 3)
    data_write_level[[j]]$conditionHeadN <- rep(data_write[[j]]$conditionHeadN[1], 3)
    data_write_level[[j]]$user<- rep(data_write[[j]]$workerId[1], 3)
  }
  
  data_write_levelAll <- rbind()
  for (d in data_write_level) {
    data_write_levelAll <- rbind(data_write_levelAll, d)
  }
  return (data_write_levelAll)
}

analyzeWritingMeansNovel<- function (data_write) {
  data_write_level <- list()
  for (j in 1:length(data_write)) {
    data_write_level[[j]] <- data_write[[j]][data_write[[j]]$seenInTraining== "false",] %>% group_by(workerId, level, conditionHeadN, conditionCE) %>% summarize(meanC = mean(correctness))
    data_write_level[[j]]$conditionCE <- rep(data_write[[j]]$conditionCE[1], 3)
    data_write_level[[j]]$conditionHeadN <- rep(data_write[[j]]$conditionHeadN[1], 3)
    data_write_level[[j]]$user<- rep(data_write[[j]]$workerId[1], 3)
  }
  
  data_write_levelAll <- rbind()
  for (d in data_write_level) {
    data_write_levelAll <- rbind(data_write_levelAll, d)
  }
  return (data_write_levelAll)
}

allDataWriteMeans<- analyzeWritingMeans(allDataWriteNew)
allDataWriteMeansUnseen<- analyzeWritingMeansNovel(allDataWriteNew)
#levels(allDataWriteMeans$level) <- c("1 item", "2 items", "3 items")
#levels(allDataWriteMeansUnseen$level) <- c("2 items", "3 items", "4 items")
```


```{r}
allDataWriteMerged <-rbind()

for (k in allDataWriteNew) {
  consonants <- c()
  for (n in 1:nrow(k)) {
consonants <- c(consonants, paste0(as.character(k$encodingCompositional[1:4]), collapse = "")) }
  k <- k[,c('workerId', 'conditionCE', 'conditionHeadN', 'level', 'arrayTraining', "seenInTraining", "participantText" , "compositionalAnswer", "encodingCorrected","encodingCompositional", "correctness")]
  k <- cbind(k, consonants)
    allDataWriteMerged <- rbind(allDataWriteMerged, k)
}
```


```{r}
allDataWriteMerged$conditionCE <- as.character(allDataWriteMerged$conditionCE)
allDataWriteMerged$conditionCE <- factor(allDataWriteMerged$conditionCE)
allDataWriteMerged$conditionHeadN <- as.character(allDataWriteMerged$conditionHeadN)
allDataWriteMerged$conditionHeadN <- factor(allDataWriteMerged$conditionHeadN)
analyzeWritingMeansN<- function (data_write, lev) {
  data_write_level <- list()
  for (j in 1:length(data_write)) {
    if (nrow(data_write[[j]]) > 1) {
    data_write_level[[j]] <- data_write[[j]] %>% group_by(level) %>% summarize(meanC = mean(correctness))
    data_write_level[[j]]$condition <- rep(data_write[[j]]$condition[1], lev)
    data_write_level[[j]]$conditionCE <- rep(data_write[[j]]$conditionCE[1], lev)
    data_write_level[[j]]$conditionHeadN <- rep(data_write[[j]]$conditionHeadN[1], lev)
    data_write_level[[j]]$user<- rep(data_write[[j]]$workerId[1], lev)
    }
    }
  data_write_levelAll <- rbind()
  for (d in data_write_level) {
    data_write_levelAll <- rbind(data_write_levelAll, d)
  }
  return (data_write_levelAll)
}
writeList <- split(allDataWriteMerged, f = allDataWriteMerged$workerId)
allDataWriteMeansNormed <- analyzeWritingMeansN(writeList, 4)
```


# Analyses and graph for resultant score of production correctness
Setting up for Helmert contrasts, as with testing data
```{r}
allDataWriteMerged$conditionCE <- as.character(allDataWriteMerged$conditionCE)

allDataWriteMerged$conditionHeadN <- as.character(allDataWriteMerged$conditionHeadN)
allDataWriteMerged$conditionHeadN <- factor(allDataWriteMerged$conditionHeadN)

allDataWriteMerged$conditionCE <- factor(allDataWriteMerged$conditionCE)
allDataWriteMerged$conditionCE <- relevel(allDataWriteMerged$conditionCE, "crossed")
allDataWriteMerged$conditionCE <- relevel(allDataWriteMerged$conditionCE, "branching")
#arrange for Helmert contrasts
contrasts(allDataWriteMerged$conditionCE) <- contr.helmert(3)
contrasts(allDataWriteMerged$conditionHeadN) <- contr.sum(2)
```

All arrays: 
```{r}
allDataWriteMerged$level <- as.numeric(allDataWriteMerged$level)
writeLmerNormed <- lmer(correctness ~ as.numeric(level-1)* conditionCE * conditionHeadN + (1 +as.numeric(level-1)|workerId), data = allDataWriteMerged)
```

Alternative with successive diffs contrast for level: 
```{r}
library(MASS)
allDataWriteMerged1 <- allDataWriteMerged
allDataWriteMerged1$level <- as.factor(allDataWriteMerged1$level)
contrasts(allDataWriteMerged1$level) <- contr.sdif(4)
writeLmerNormed2 <- lmer(correctness ~ level* conditionCE * conditionHeadN + (1 +level|workerId), data = allDataWriteMerged1)
```

Level 4 alone
```{r}

allDataWriteMerged4 <- allDataWriteMerged[allDataWriteMerged$level == 4,]
allDataWriteMerged4$level <- as.factor(allDataWriteMerged4$level)
writeLmerNormed4 <- lmer(correctness ~ conditionCE * conditionHeadN + (1|workerId), data = allDataWriteMerged4)
summary(writeLmerNormed4)
```

Seen vs. unseen: 
```{r  message=FALSE,warning = FALSE}
adwM23 <- allDataWriteMerged[allDataWriteMerged$level %in% c(2,3),]
contrasts(adwM23$conditionCE) <- contr.helmert(3)
adwM23$seenInTraining <-as.factor(adwM23$seenInTraining)
adwM23$seenInTraining <- relevel(adwM23$seenInTraining , "false")
adwM23$level <- as.factor(adwM23$level)
contrasts(adwM23$seenInTraining) <- contr.sum(2)
writeLmerNormedSeen <- lmer(correctness ~ level* conditionCE * conditionHeadN * seenInTraining+ (1 +level|workerId), data = adwM23)
```

Seen only, and unseen only: 
```{r  message=FALSE, warning=FALSE}
adwmSeen <- allDataWriteMerged[allDataWriteMerged$seenInTraining == "true",]
adwmUnSeen <- allDataWriteMerged[allDataWriteMerged$seenInTraining == "false",]
adwmSeen$level <- as.factor(adwmSeen$level)
adwmUnSeen$level <- as.factor(adwmUnSeen$level)
adwmSeen$level <- factor(adwmSeen$level, levels = c(1,2,3))
adwmUnSeen$level <- factor(adwmUnSeen$level, levels = c(2,3,4))
contrasts(adwmSeen$level) <- contr.sdif(3)
contrasts(adwmUnSeen$level) <- contr.sdif(3)
contrasts(adwmSeen$conditionCE) <- contr.helmert(3)
contrasts(adwmSeen$conditionHeadN) <- contr.sum(2)
contrasts(adwmUnSeen$conditionCE) <- contr.helmert(3)
contrasts(adwmUnSeen$conditionHeadN) <- contr.sum(2)
writeLmerNormedAllSeen <- lmer(correctness ~ level* conditionCE * conditionHeadN + (1 +level|workerId), data = adwmSeen)
writeLmerNormedAllNoSeen <- lmer(correctness ~ level* conditionCE * conditionHeadN + (1 +level|workerId), data = adwmUnSeen)
```


#Production graph 
```{r  message=FALSE,warning= FALSE}
analyzeWritingMeansNSeen<- function (data_write, lev) {
  data_write_level <- list()
  for (j in 1:length(data_write)) {
    data_write_level[[j]] <- data_write[[j]] %>% group_by(level, seenInTraining) %>% summarize(meanC = mean(correctness))
    data_write_level[[j]]$condition <- rep(data_write[[j]]$condition[1], lev)
    data_write_level[[j]]$conditionCE <- rep(data_write[[j]]$conditionCE[1], lev)
    data_write_level[[j]]$conditionHeadN <- rep(data_write[[j]]$conditionHeadN[1], lev)
    data_write_level[[j]]$user<- rep(data_write[[j]]$workerId[1], lev)
  }
  
  data_write_levelAll <- rbind()
  for (d in data_write_level) {
    data_write_levelAll <- rbind(data_write_levelAll, d)
  }
  return (data_write_levelAll)
}
adwmSeenUnseen <- analyzeWritingMeansNSeen(writeList, 6)
adwmSeenUnseen$conditionCE <- as.factor(adwmSeenUnseen$conditionCE)
adwmSeenUnseen$conditionHeadN <- relevel(adwmSeenUnseen$conditionHeadN, "noun initial", "noun final")
adwmSeenUnseen$conditionCE <- relevel(adwmSeenUnseen$conditionCE, "crossed")
adwmSeenUnseen$conditionCE <- relevel(adwmSeenUnseen$conditionCE, "center-embedding")
adwmSeenUnseen$group <- as.factor(paste0(adwmSeenUnseen$level, adwmSeenUnseen$seenInTraining))
adwmSeenUnseen$group <- relevel(adwmSeenUnseen$group, "3true")
adwmSeenUnseen$group <- relevel(adwmSeenUnseen$group, "2false")
adwmSeenUnseen$group <- relevel(adwmSeenUnseen$group, "2true")
adwmSeenUnseen$group <- relevel(adwmSeenUnseen$group, "1true")
ggplot(adwmSeenUnseen, aes(x= group, y= meanC, fill = level))+
  stat_summary(aes(fill = level, group=1), fun= "mean", geom="point", pch = 23, size = 3) +
  geom_dotplot(binaxis='y',stackdir='center', alpha = .5)+
  facet_grid(conditionCE ~ conditionHeadN )+
  ylab("Mean correctness")+
  theme_bw()+ 
  theme(legend.position = "none")+
  scale_fill_discrete(name = "level", labels = c("1", "2 seen", "2 unseen", "3 seen","3 unseen", "4"))+ 
  scale_x_discrete(name = "level", labels = c("1", "2 seen", "2 unseen", "3 seen","3 unseen", "4"))
```


# Merging adposition data with writing data 

```{r}
prepMGloss <-c()
prepRGloss <- c()
for (w in unique(allDataWriteMerged$workerId)) {
  writeCount = nrow(allDataWriteMerged[allDataWriteMerged$workerId == w,])
  prepMGloss <- c(prepMGloss, rep(as.character(prepList$PH[prepList$workerId == w]), each = writeCount))
  prepRGloss <- c(prepRGloss, rep(as.character(prepList$PV[prepList$workerId== w]), each = writeCount))
}
allDataWriteMerged <- cbind(allDataWriteMerged, prepMGloss, prepRGloss)
write.csv(allDataWriteMerged, paste0(getwd(), 'allDataWriteMerged.csv'))
```

The resulting CSV is then fed through the python file "array to caption syntax orders" 

Output models to HTML
```{r  message=FALSE, warning=FALSE}
library(sjPlot)
a<- as.data.frame(coefficients(summary(testLmerInteract2)))
rownames(a) <-gsub("Intercept", "level 2/branching/head-initial", rownames(a))
rownames(a) <-gsub("level3", "level 3", rownames(a))
rownames(a) <-gsub("conditionCE1", "crossed", rownames(a))
rownames(a) <-gsub("conditionCE2", "crossed/CE mean", rownames(a))
rownames(a) <-gsub("conditionHeadN1", "head-final", rownames(a))
rownames(a) <-gsub(":", "/", rownames(a))

b<- as.data.frame(coefficients(summary(writeLmerNormed)))
rownames(b) <-gsub("Intercept", "level 1/branching/head-initial", rownames(b))
rownames(b) <-gsub("as.numeric\\(level - 1\\)", "level", rownames(b))
rownames(b) <-gsub("conditionCE1", "crossed", rownames(b))
rownames(b) <-gsub("conditionCE2", "crossed/ CE mean", rownames(b))
rownames(b) <-gsub("conditionHeadN1", "head-final", rownames(b))
rownames(b) <-gsub(":", "/", rownames(b))

b2<- as.data.frame(coefficients(summary(writeLmerNormed2)))
rownames(b2) <-gsub("Intercept", "level 1/branching/head-initial", rownames(b2))
rownames(b2) <-gsub("conditionCE1", "crossed", rownames(b2))
rownames(b2) <-gsub("conditionCE2", "crossed/ CE mean", rownames(b2))
rownames(b2) <-gsub("conditionHeadN1", "head-final", rownames(b2))
rownames(b2) <-gsub(":", "/", rownames(b2))

c<- as.data.frame(coefficients(summary(writeLmerNormedSeen)))

rownames(c) <-gsub("Intercept", "level 2/branching/head-initial/seen", rownames(c))

rownames(c) <-gsub("level3", "level 3", rownames(c))
rownames(c) <-gsub("conditionCE1", "crossed", rownames(c))
rownames(c) <-gsub("conditionCE2", "center-embedded", rownames(c))
rownames(c) <-gsub("conditionHeadN1", "head-final", rownames(c))
rownames(c) <-gsub("seenInTraining1", "unseen", rownames(c))
rownames(c) <-gsub(":", "/", rownames(c))
d<- as.data.frame(coefficients(summary(writeLmerNormedAllSeen)))
rownames(d) <-gsub("Intercept", "level 1/branching/head-initial", rownames(d))
rownames(d) <-gsub("as.numeric\\(level - 1\\)", "level", rownames(d))
rownames(d) <-gsub("conditionCE1", "crossed", rownames(d))
rownames(d) <-gsub("conditionCE2", "center-embedded", rownames(d))
rownames(d) <-gsub("conditionHeadN1", "head-final", rownames(d))
rownames(d) <-gsub(":", "/", rownames(d))

e<- as.data.frame(coefficients(summary(writeLmerNormedAllNoSeen)))
rownames(e) <-gsub("Intercept", "level 2/branching/head-initial", rownames(e))
rownames(e) <-gsub("as.numeric\\(level - 1\\)", "level", rownames(e))
rownames(e) <-gsub("3-2", "4-3", rownames(e))
rownames(e) <-gsub("2-1", "3-2", rownames(e))
rownames(e) <-gsub("conditionCE1", "crossed", rownames(e))
rownames(e) <-gsub("conditionCE2", "center-embedded", rownames(e))
rownames(e) <-gsub("conditionHeadN1", "head-final", rownames(e))
rownames(e) <-gsub(":", "/", rownames(e))
library(sjmisc)
allModels <- list(a, b, c, d, e)
for (i in 1:length(allModels)) {
  allModels[[i]] <- round_num(allModels[[i]], 3)
allModels[[i]][,ncol(allModels[[i]])][allModels[[i]][,ncol(allModels[[i]])] == 0] <- "< .001"
}
titles = c("Comprehension task","Production task", "Seen vs. unseen arrays", "Production task: seen only", "Production task: novel only")
tab_dfs(allModels, titles = titles, show.rownames = TRUE, file = paste0(getwd(), 'tables.html'))
```
