---
title: 'Experiment 1: Learnability (3 syntax conditions, adposition training): Grammars'
output:
  html_document: default
  pdf_document: default
---

## Import grammar file

Grammar file is imported. "grammars" contains interpretations of every array in every grammar. 
```{r  message=FALSE, warning=FALSE}
library(stringdist)
library (tidyverse)
library(lmerTest)
setwd("/Users/emilydavis/Desktop/paper data/Experiment1Learnability")
allDataWriteMerged2 <-read.csv(paste0(getwd(), '/allDataWriteMergedGrammars.csv'))
```

Manually cleaning up some entries where write-in answers are synonymous with "left" or "Horizontal." 
```{r}
allDataWriteMerged2$prepMGloss <- as.character(allDataWriteMerged2$prepMGloss)
  allDataWriteMerged2$prepMGloss[allDataWriteMerged2$workerId == "A108"] <- "horiz"
  allDataWriteMerged2$prepMGloss[allDataWriteMerged2$workerId == "A99"] <- "horiz"
  
  allDataWriteMerged2$prepMGloss[allDataWriteMerged2$workerId == "A7"] <- "none"
  allDataWriteMerged2$prepMGloss[allDataWriteMerged2$workerId == "A25"] <- "left"
  
```

 "grammars" contains interpretations of every array in every grammar. 
```{r}
grammarcols <- c()
for (c in colnames(allDataWriteMerged2)) {
  if (grepl("Grammar", c) == TRUE)
    grammarcols <- c(grammarcols, c)
}
grammars <- allDataWriteMerged2[, grammarcols]
```

## Find the best-fit grammar(s) for each string
comparing the string to each of the corresponding strings from possible grammars. If there's no sufficiently close grammar, the string is declared uninterpretable. 
```{r}
closestGram <- list()
for (n in 1:nrow(allDataWriteMerged2)) {
  comparisons <- c()
  for (k in 1:ncol(grammars)) {
    input <- as.character(allDataWriteMerged2$encodingCorrected[n])
    comp <- as.character(grammars[n,k])
    ds <- stringdist(input, comp, method = "osa")/max(nchar(input), nchar(comp))
    comparisons <- c(comparisons, ds)
    if (min(comparisons) > .75) {
      closestGram[[n]] <- "X"
    } else {
   closest <- which(comparisons == min(comparisons))
  closestGram[[n]] <- grammarcols[closest]
    }
    }
  }

clGram <- c()
for (n in 1:length(closestGram)) {
  cl <- paste(closestGram[[n]], collapse = ' ')
  clGram <- c(clGram, cl)
}
allDataWriteMerged2 <- cbind(allDataWriteMerged2, clGram)
```

Next: filter out grammars that don't fit with the user's self-reported adposition meanings. If meanings given are ambiguous or uninterpretable, no grammars will be discarded as all are possibly valid. 

```{r}
clGramsFiltered <- c()
possibleGrammars <- c()
for (n in 1:nrow(allDataWriteMerged2)) {
  grams <- strsplit(as.character(allDataWriteMerged2$clGram[n]), " ")[[1]]
  gramsRemove <- c()
  #remove wrong orientation
if (allDataWriteMerged2$prepRGloss[n] %in% c("horiz", "left", "right")) {
    for (gram in grams) {
      if (grepl("r.Atop|r.Vert|r.Under", gram) == TRUE) {
        gramsRemove <- c(gramsRemove, gram)
      }
    }
 #remove contradicting answers 
if (allDataWriteMerged2$prepRGloss[n] == "right") {
    for (gram in grams) {
      if (grepl("r.Left", gram) == TRUE) {
        gramsRemove <- c(gramsRemove, gram)
      }
    }
}
else if (allDataWriteMerged2$prepRGloss[n] == "left") {
    for (gram in grams) {
      if (grepl("r.Right", gram) == TRUE) {
        gramsRemove <- c(gramsRemove, gram)
      }
    }
}
  
 }
else if (allDataWriteMerged2$prepRGloss[n] %in% c("atop", "vert", "under")) {
    for (gram in grams) {
      if (grepl("r.Left|r.Right|r.Horiz", gram) == TRUE) {
        gramsRemove <- c(gramsRemove, gram)
      }
    }
    if (allDataWriteMerged2$prepRGloss[n] == "under") {
    for (gram in grams) {
      if (grepl("r.Atop", gram) == TRUE) {
        gramsRemove <- c(gramsRemove, gram)
      }
    }
}
else if (allDataWriteMerged2$prepRGloss[n] == "atop") {
    for (gram in grams) {
      if (grepl("r.Under", gram) == TRUE) {
        gramsRemove <- c(gramsRemove, gram)
      }
    }
}
  else {#vertical not specified
    if (allDataWriteMerged2$prepMGloss[n] == "left") {
  for (gram in grams) {
      if (grepl("m.Right", gram) == TRUE) {
        gramsRemove <- c(gramsRemove, gram)
      }
  }
} else if (allDataWriteMerged2$prepMGloss[n] == "right") {
  for (gram in grams) {
      if (grepl("m.Left", gram) == TRUE) {
        gramsRemove <- c(gramsRemove, gram)
      }
    }
  }
  }
  }
  

#do the same for other adposition   
  #remove wrong orientation


   if (length(grams) > length(gramsRemove)) { #if all possible grammars are ruled out, just keep them
  gramsFiltered = grams[!grams %in% gramsRemove]
   } else {
     gramsFiltered = grams
   }
  gm <- paste(gramsFiltered, collapse = " ")
  clGramsFiltered <- c(clGramsFiltered, gm)
  possibleGrammars <- c(possibleGrammars, length(gramsFiltered))
}
allDataWriteMerged2 <- cbind(allDataWriteMerged2, clGramsFiltered, possibleGrammars)
```

## Features

Deconstruct the grammars into features. 

```{r}
featureType1 <- c() #CE, noCE, crossed
for (i in 1:nrow(allDataWriteMerged2)) {
  gs<- strsplit(as.character(allDataWriteMerged2$clGramsFiltered[i]), " ")[[1]]
  types <- c()
   for (g in gs) {
  types <- c(types, str_extract(g, "CE|noCE|Crossed|X"))
  types <- unique(types)
    if (length(types) >= 2) {
      if (length(types) == 2 && "CE" %in% types && "Crossed" %in% types) {
        t <- paste0(types, collapse = " or ")
      } else {
    t <- "X"
    }
    } else {
    t <- paste0(types, collapse = " ")
    }
}
  featureType1 <- c(featureType1, t)
}

featureHead1 <- c() 
for (i in 1:nrow(allDataWriteMerged2)) {
  gs<- strsplit(as.character(allDataWriteMerged2$clGramsFiltered[i]), " ")[[1]]
  heads <- c()
   for (g in gs) {
 heads <- c(heads, str_extract(g, "Initial|Final|X"))
  heads <- unique(heads)
    if (length(heads) >= 2 || "X" %in% heads) {
 	t <-"indeterminate"
    } else {
    t <- paste0(heads, collapse = " ")
    }
}
  featureHead1 <- c(featureHead1, t)
}

allDataWriteMerged2 <- cbind(allDataWriteMerged2, featureType1, featureHead1)

allDataWriteMerged2$featureType1 <- as.character(allDataWriteMerged2$featureType1)
allDataWriteMerged2$featureHead1 <- as.character(allDataWriteMerged2$featureHead1)
```

```{r}
allDataWriteMerged2 <- select(allDataWriteMerged2[allDataWriteMerged2$level != 1,], workerId, conditionCE, conditionHeadN, level, seenInTraining, arrayTraining, featureHead1, featureType1, clGramsFiltered)
```

Some data missing for one worker. Fill these in as uninterpretable 

```{r  message=FALSE, warning=FALSE}
library(data.table)
allDataWriteMerged2$item2 <- as.integer(as.factor(allDataWriteMerged2$arrayTraining))
DT = as.data.table(allDataWriteMerged2)
setkey(DT,workerId, item2)
DT <- DT[CJ(unique(workerId),seq(min(item2),max(item2)))]

DT <- replace_na(DT, list(conditionCE = "branching", conditionHeadN = "head initial", featureType1 = "X", featureHead1 = "indeterminate", clGramsFiltered = " "))
#still NA
DT <- as.data.frame(DT)
nas <- as.numeric(rownames(DT))[is.na(DT$level)]
for (n in nas) {
  for (k in 4:6) {
  DT[n,k] <- DT[n-36,k]
  }
}
allDataWriteMerged2 <- DT
```

```{r}
#give each worker in-group a number
allDataWriteMerged2 <- arrange(allDataWriteMerged2, conditionCE, conditionHeadN, workerId, level, desc(seenInTraining), item2)
worker <- c()
for (w in 1:120) {
  writeCount = nrow(allDataWriteMerged2[allDataWriteMerged2$workerId == unique(allDataWriteMerged2$workerId)[w],])
  worker <- c(worker, rep(w %%20, writeCount))

}
item <- c()
for (w in unique(allDataWriteMerged2$workerId)) {
  writeCount = nrow(allDataWriteMerged2[allDataWriteMerged2$workerId == w,])
  item <- c(item, 1:writeCount)

}
allDataWriteMerged2 <- cbind(allDataWriteMerged2, item)
allDataWriteMerged2 <- cbind(allDataWriteMerged2, worker)
```

## Graph of syntax type by condition

```{r  message=FALSE, warning=FALSE}
library(scales)
allDataWriteMerged2$level <- as.factor(allDataWriteMerged2$level)
allDataWriteMerged2$conditionHeadN <- as.factor(allDataWriteMerged2$conditionHeadN)
allDataWriteMerged2$conditionCE <- as.factor(allDataWriteMerged2$conditionCE)
allDataWriteMerged2$worker <- as.factor(as.character(allDataWriteMerged2$worker))
allDataWriteMerged2$conditionHeadN <- relevel(allDataWriteMerged2$conditionHeadN, "head initial", "head final")
allDataWriteMerged2$conditionCE <- relevel(allDataWriteMerged2$conditionCE, "crossed")
allDataWriteMerged2$conditionCE <- relevel(allDataWriteMerged2$conditionCE, "center-embedding")
```

```{r}
p<- ggplot( allDataWriteMerged2[allDataWriteMerged2$level != 1,], aes(x = worker, y = as.factor(item), fill = featureType1)) +
  facet_grid(conditionCE ~ conditionHeadN)+
  geom_bin2d()+
  scale_y_discrete(labels = c(rep("", 3), "2 seen", rep("", 5),"2 new", rep("", 5),"3 seen", rep("", 5),"3 new", rep("", 7),"4 new", rep("", 6)))+
  labs(fill = "Syntax Type", shape = "Head Order")+
  scale_fill_manual(labels = c("Center-embedded", "Center-embedded/Crossed","Crossed", "Branching", "Uninterpretable"),  values =  hue_pal()(5)) +
    geom_hline(yintercept=8.5, size = .3, alpha = .6)+ #blocking off levels and seen/unseen: 2 seen
    geom_hline(yintercept=12.5, size = .3, alpha = .6)+ #blocking off levels and seen/unseen 2 new
  geom_hline(yintercept=20.5, size = .3, alpha = .6)+ #blocking off levels and seen/unseen 3 seen
  geom_hline(yintercept=24.5, size = .3, alpha = .6)+ 
  #blocking off levels and seen/unseen 3 new/4 new
 geom_point(aes(shape = featureHead1, color = featureHead1), size = 1)+
  scale_shape_manual(labels = c("Final", "Indeterminate", "Initial"),  values =c(4, NA, 1)) +
  scale_color_manual(labels = c("Final", "Indeterminate", "Initial"),  values =c("black", NA, "black"), guide = FALSE)+ 
  theme_bw()+
  guides(fill = guide_legend(override.aes = list(shape = NA)))+
  theme(axis.ticks.y = element_blank(), 
        axis.ticks.x = element_blank(), axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank())
  ggsave(paste0(getwd(), "/syntax_strings_condition.png"), p, width=9, height=10)
```
