---
title: "Pilot Experiment 2: Iterated Learning"
output: html_document
fig_crop: no
---

```{r setup, include=FALSE,  message=FALSE, warning=FALSE}
options(warn=-1)
library(MASS)
library (tidyverse)
library(lubridate)
library(stringdist)
library(lme4)
library(lmerTest)
```

## Needed functions
Create dataframes for compehension tests and write-in data. 

```{r results='hide', message=FALSE, warning=FALSE}

analyze<- function(datas) {
  dataTesting <-list()
  scores <- c()
  for (i in 1:length(datas)) {
    dataTesting[[i]] <- datas[[i]][datas[[i]]$trialType == "testing",]
    dataTesting[[i]]$participantChoiceNumber[is.na(dataTesting[[i]]$participantChoiceNumber)] <- "X"
    dataTesting[[i]]$correct = dataTesting[[i]]$correctChoiceNumber == dataTesting[[i]]$participantChoiceNumber
  }
  return(dataTesting)
}

analyzeMeanTesting <- function(dataTesting) {
  dataTestingLevel <- list()
  for (i in 1:length(dataTesting)) {
    dataTestingLevel[[i]] <- dataTesting[[i]] %>%
      group_by(level)  %>% 
      summarize(level_score = sum(correct)/length(correct))
    dataTestingLevel[[i]]$chain <- rep(dataTesting[[i]]$chain[1], nrow(dataTestingLevel[[i]]))
    dataTestingLevel[[i]]$generation <- rep(dataTesting[[i]]$generation[1], nrow(dataTestingLevel[[i]]))
    dataTestingLevel[[i]]$user <- rep(dataTesting[[i]]$workerId[1], nrow(dataTestingLevel[[i]]))
  }
  dataTestingLevelAllUsers <- rbind()
  for (dat in dataTestingLevel) {
    dataTestingLevelAllUsers <- rbind(dataTestingLevelAllUsers, dat)
  }
  return(dataTestingLevelAllUsers)
}

analyzeWriting <- function(datas) {
  #compositional answers analysis
  data_write <- list()
  data_write_level <- list()
  for (i in 1:length(datas)) {
    dataWriteNew <- datas[[i]][datas[[i]]$trialType == "write",]
    dataWriteNew$participantText[is.na(dataWriteNew$participantText)] <- ""
      #print(dataWriteNew$participantText)
      
      data_write[[length(data_write) +1]] <- dataWriteNew
  }
  
  return (data_write)
}


```

## Processing the data
Import task data and demographic files, which have been anonymized. 

```{r results='hide', message=FALSE, warning=FALSE}

setwd("/Users/emilydavis/Desktop/paper data/pilotExperIter")
dataAnon <- read.csv(paste0(getwd(), '/allDataAnonPilotIter1.csv'))
dataFiles <- split(dataAnon, dataAnon$workerId)

allDataTesting <- analyze(dataFiles)
allDataTestingMerged <- rbind()
for (dat in allDataTesting) {
  allDataTestingMerged <- rbind(allDataTestingMerged, dat)
}
allDataTestingLevel <- analyzeMeanTesting(allDataTesting)
allDataTestingMean <- allDataTestingLevel %>% group_by(chain, generation, level) %>% summarize(level_score = mean(level_score))

allDataWrite <- analyzeWriting(dataFiles)

```


## Comprehension

Graph and analysis

```{r results='hide', message=FALSE, warning=FALSE}
allDataTestingLevel$level <- as.factor(allDataTestingLevel$level )
levels(allDataTestingLevel$level) <- c("1 item", "2 items", "3 items")
ggplot(allDataTestingLevel, aes(x= generation, y= level_score, color = chain, alpha = .5)) +
  geom_line()+
  facet_wrap(~level, ncol=1)+
  scale_x_discrete(name ="generation", 
                    limits=1:10)+
  stat_summary(aes(colour="mean",group=1), fun.y= "mean", geom="line", color = "black", alpha = 1)+
   guides(alpha = FALSE)+
  ylab("Proportion correct")+
  theme_bw()+
  theme(legend.position = "none")

```



```{r}

allDataTestingMerged$level <- as.factor(allDataTestingMerged$level)
contrasts(allDataTestingMerged$level) <- contr.sdif(3)
testLmerInteract <- glmer(correct ~ level* generation +(1 + level | chain:workerId) + (1 + generation | chain), data = allDataTestingMerged, family = "binomial")
```



## Production accuracy

Combine all writing trials, and get initials. 
```{r warning = FALSE, message= FALSE}
allDataWriteNew <- list()
for (d in allDataWrite) {
encodingCorrected <- c()
for (i in 1:nrow(d)) {
  splitC <- strsplit(as.character(d$participantText[i]), " ")[[1]]
  initialsC <- c()
  for (word in splitC) {
    initialsC <- c(initialsC, substring(word, 1, 1))
  }
  initC <- paste(initialsC, collapse = "")
  encodingCorrected <- c(encodingCorrected, initC)
}
encodingCompositional <- c()
for (i in 1:nrow(d)) {
  splitC <- strsplit(as.character(d$compositionalAnswer[i]), " ")[[1]]
  initialsC <- c()
  for (word in splitC) {
    initialsC <- c(initialsC, substring(word, 1, 1))
  }
  initC <- paste(initialsC, collapse = "")
  encodingCompositional<- c(encodingCompositional, initC)
}
d <-cbind(d, encodingCorrected, encodingCompositional)
correctness <- c()
for (i in 1:nrow(d)) {
  longer = max( 
nchar(as.character(d$encodingCompositional[i])), nchar(as.character(d$encodingCorrected[i])) )
  normedC <- 1- (stringdist(as.character(d$encodingCompositional[i]),
                            as.character(d$encodingCorrected[i]),
                                      method = "osa")/longer)
  correctness <-c(correctness, normedC) 
}
d <- cbind(d, correctness)
allDataWriteNew[[length(allDataWriteNew)+1]] <- d
}

analyzeWritingMeans<- function (data_write) {
  data_write_level <- list()
  for (j in 1:length(data_write)) {
    data_write_level[[j]] <- data_write[[j]][data_write[[j]]$seenInTraining== "true",] %>% group_by(workerId, level, chain, generation, seenInTraining) %>% summarize(meanC = mean(correctness))
    data_write_level[[j]]$generation <- rep(data_write[[j]]$generation[1], 3)
    data_write_level[[j]]$chain <- rep(data_write[[j]]$chain[1], 3)
    data_write_level[[j]]$user<- rep(data_write[[j]]$workerId[1], 3)
  }
  
  data_write_levelAll <- rbind()
  for (d in data_write_level) {
    data_write_levelAll <- rbind(data_write_levelAll, d)
  }
  return (data_write_levelAll)
}

analyzeWritingMeansNovel<- function (data_write) {
  data_write_level <- list()
  for (j in 1:length(data_write)) {
    data_write_level[[j]] <- data_write[[j]][data_write[[j]]$seenInTraining== "false",] %>% group_by(workerId, level, chain, generation, seenInTraining) %>% summarize(meanC = mean(correctness))
    data_write_level[[j]]$generation <- rep(data_write[[j]]$generation[1], 3)
    data_write_level[[j]]$chain <- rep(data_write[[j]]$chain[1], 3)
    data_write_level[[j]]$user<- rep(data_write[[j]]$workerId[1], 3)
  }
  
  data_write_levelAll <- rbind()
  for (d in data_write_level) {
    data_write_levelAll <- rbind(data_write_levelAll, d)
  }
  return (data_write_levelAll)
}

allDataWriteMeans<- analyzeWritingMeans(allDataWriteNew)
allDataWriteMeansUnseen<- analyzeWritingMeansNovel(allDataWriteNew)
levels(allDataWriteMeans$level) <- c("1 item", "2 items", "3 items", "4 items")
levels(allDataWriteMeansUnseen$level) <- c("1 item", "2 items", "3 items", "4 items")
```

```{r}
allDataWriteMeans2 <- rbind(allDataWriteMeans, allDataWriteMeansUnseen)
allDataWriteMeans2$seenInTraining <- as.character(allDataWriteMeans2$seenInTraining)
allDataWriteMeans2$level <- allDataWriteMeans2$level +1
allDataWriteMeans2$seenInTraining[allDataWriteMeans2$seenInTraining == "true"] <- "seen"
allDataWriteMeans2$seenInTraining[allDataWriteMeans2$seenInTraining == "false"] <- "unseen"
ggplot(allDataWriteMeans2, aes(x= generation, y= meanC, color = chain, alpha = .5)) +
  geom_line()+
  stat_summary(aes(colour="mean",group=1), fun= "mean", geom="line", color = "black", alpha = 1)+
   guides(alpha = FALSE)+
    facet_grid(rows = vars(level), cols = vars(seenInTraining))+
  scale_x_discrete(name ="generation", 
                    limits=factor(1:10))+
   guides(alpha = FALSE)+
  ggtitle("")+ 
  ylab("Correctness")+
  theme_bw()+
  theme(legend.position = "none")
```
```{r  message=FALSE, warning=FALSE}
library(MASS)
allDataWriteMeans$level <- factor(allDataWriteMeans$level)
allDataWriteMeansUnseen$level <- factor(allDataWriteMeansUnseen$level)
contrasts(allDataWriteMeans$level) <- contr.sdif(3)
contrasts(allDataWriteMeansUnseen$level) <- contr.sdif(3)
modelConsistencySeen <- lmer(meanC ~ level* generation + (1+generation * level | chain), data = allDataWriteMeans)
modelConsistencyUnseen <- lmer(meanC ~  level* generation + (1+generation * level | chain), data = allDataWriteMeansUnseen)
```

## Analysis of writing: matching possible grammars 
Merge relevant columns of writing files into one big file

```{r}
allDataWriteMerged <-rbind()

chain <- c()
consonants <- c()
for (k in allDataWriteNew) {
   if (k$generation[1] == 1) {#make generation 0 tables
  consonants <- c(consonants, paste0(k$encodingCompositional[1:4], collapse = ''))
  chain<- c(chain, as.character(k$chain[1]))
   }
}
consonantsChain <- data.frame(chain = as.character(chain), consonants)
#needs to also include generation 0 
for (k in allDataWriteNew) {
  #take initials of first four participant entries; these are their noun names
  p = strsplit(as.character(k$participantText[k$arrayTraining == "0"]), '')[[1]][1]
  for (j in 1:3) {
    p = paste0(p, strsplit(as.character(k$participantText[k$arrayTraining == as.character(j)]), '')[[1]][1])
  }
  #add to the data frame
  nounsUser <- rep(p, nrow(k))
  k <- cbind(k, nounsUser)
  #"canonical" nouns of chain, at gen0
  consonantsChain2 <- as.character(consonantsChain$consonants[consonantsChain$chain == k$chain[1]])
  k <- cbind(k, lexiconChain = rep(consonantsChain2, nrow(k)))
  k2 <- k[, c("workerId", "chain", "generation", "level", "arrayTraining", "encodingCorrected", "nounsUser", "lexiconChain", "seenInTraining")]
  #merge everything together
  allDataWriteMerged <-rbind(allDataWriteMerged, k2)
  if (k$generation[1] == 1) {#make generation 0 tables
    name = paste0(as.character(k$chain[1]), "_0")
    k3 <- data.frame(workerId = rep(name, nrow(k)), generation = rep(0, nrow(k)), chain = k$chain, level = k$level, arrayTraining = k$arrayTraining,
                     encodingCorrected = k$encodingCompositional, #captions seen by user at gen 1
                     nounsUser = k$lexiconChain,
                     lexiconChain = k$lexiconChain,
                     seenInTraining = k$seenInTraining)
    allDataWriteMerged <- rbind(allDataWriteMerged, k3)
  }
}
#each user's names for the items, plus their prepositions
lexiconUser <- c()
for (n in 1:nrow(allDataWriteMerged)) {
lexiconUser <- c(lexiconUser, paste0(allDataWriteMerged$lexiconChain[n], "mr"))
}
allDataWriteMerged <- cbind(allDataWriteMerged, lexiconUser)
prepsUser <- c()
for (n in 1:nrow(allDataWriteMerged)) {
  prepsUser <- c(prepsUser, paste0(str_extract_all(lexiconUser, paste0('[^',allDataWriteMerged$nounsUser[n], ']'))[[1]], collapse = ''))
}
allDataWriteMerged <- cbind(allDataWriteMerged, prepsUser)
allDataWriteMerged <- dplyr::select(allDataWriteMerged, workerId, chain, generation, level, arrayTraining, encodingCorrected, nounsUser, prepsUser, seenInTraining)
allDataWriteMerged <- arrange(allDataWriteMerged, workerId)
write.csv(allDataWriteMerged, paste0(getwd(),'/allDataWritePilotIter1.csv'))
```

Then run the python code with appropriate input and output files. Note: use the "iter1" version of the file, as the code is different here to account for users' nouns and prepositions deviating from the original (i.e. adpositions reinterpreted as object names). 

Output models to HTML
```{r  message=FALSE, warning=FALSE}
library(sjPlot)
a<- as.data.frame(coefficients(summary(testLmerInteract)))
rownames(a) <-gsub("Intercept", "level 1/generation 1", rownames(a))
rownames(a) <-gsub(":", "/", rownames(a))

b<- as.data.frame(coefficients(summary(modelConsistencySeen)))
rownames(b) <-gsub("Intercept", "level 1/generation 0", rownames(b))
rownames(b) <-gsub(":", "/", rownames(b))

c<- as.data.frame(coefficients(summary(modelConsistencyUnseen)))
rownames(c) <-gsub("Intercept", "level 2/generation 1", rownames(c))
rownames(c) <-gsub("3-2", "4-3", rownames(c))
rownames(c) <-gsub("2-1", "3-2", rownames(c))
rownames(c) <-gsub(":", "/", rownames(c))
library(sjmisc)
allModels <- list(a, b,c)
for (i in 1:length(allModels)) {
  allModels[[i]] <- round_num(allModels[[i]], 3)
allModels[[i]][,ncol(allModels[[i]])][allModels[[i]][,ncol(allModels[[i]])] == 0] <- "< .001"
}
tab_dfs(allModels, titles = c("Comprehension task", "Consistency of captions: arrays seen in training", "Consistency of captions: novel arrays"), file = paste0(getwd(),  '/tables.html'))
```